New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-19 review/response.Rmd

\textcolor{blue}{This is better explained}

        – Page 8, line 11: "The most relevant inbuilt Mathematica function for our purpose is the LocatorPane. This creates a region on the screen where the position of the mouse is captured and then converted to input that updates the graphics functions, enabling the manual navigation of the tour."

    - Finally, after all of this time, this is the one input that might be a bit harder to implement in R/Shiny, though I think via WebGL it should be workable. This is where the focus should be, rather than the previous two paragraphs, which are a distraction.

\textcolor{blue}{The first two paragraphs have been removed and the third restructured to explain why this is difficult in R/Shiny/rgl.}

@@

Section 1 line 29 "The software section describes mathematica package"  mathematica should be capitalized as you did  through the paper in most cases.  Also since is the first time you have mentioned Mathematica you should include the reference here (Wolfram reference appears in page 4 line 26 for first time)

\textcolor{blue}{done}

Section 2: "manual tour allows the user to alter the coefficients of one (or more) variables" but in the explanation it is not clear what is  $V_m$  and how to alter the coefficients for more than one variable.

\textcolor{blue}{definition of $V_m$ added but have not addressed the second part of the comment TODO}

### 2023-01-19 paper/paper.Rmd
added new plots

The new approach emerged from experiments on the tour using the linear algebra capabilities, and relatively new interactive graphics interface, available in Mathematica [@Mathematica]. The components corresponding to $V_m$ are directly controlled by cursor movement, which updates row $m$ of $A$. The updated matrix is then orthonormalised.

@@

Mathematica provided a useful sandbox to experiment with the ideas presented in this paper. Most of the data, though, is first constructed using R, especially the classification boundaries. If new technology for interactive graphics becomes available in R it would be useful to create a tighter coupling of models and visualization to allow exploring and comparing fits.

>>>>

The new approach emerged from experiments on the tour using the linear algebra capabilities, and relatively new interactive graphics interface, available in Mathematica. The components corresponding to $V_m$ are directly controlled by cursor movement, which updates row $m$ of $A$. The updated matrix is then orthonormalised.

@@

Mathematica provided a useful sandbox to experiment with the ideas presented in this paper. Most of the data, though, is first constructed using R, especially the classification boundaries. If new technology for interactive graphics with precise cursor control becomes available in R it would be useful to create a tighter coupling of models and visualization to allow exploring and comparing fits.

### 2023-01-19 paper/paper.tex
added new plots

The new approach emerged from experiments on the tour using the linear
algebra capabilities, and relatively new interactive graphics interface,
available in Mathematica \citep{Mathematica}. The components
corresponding to \(V_m\) are directly controlled by cursor movement,
which updates row \(m\) of \(A\). The updated matrix is then
orthonormalised.

>>>>

The new approach emerged from experiments on the tour using the linear
algebra capabilities, and relatively new interactive graphics interface,
available in Mathematica. The components corresponding to \(V_m\) are
directly controlled by cursor movement, which updates row \(m\) of
\(A\). The updated matrix is then orthonormalised.
